MPI3

### 2018-04-23 MiP3.Rmd
Can I go home now?

# All together now 
grid.arrange(ind_limits_2010.histo, ind2pty_limits_2010.histo, pac_limits_2010.histo, CCI1, CCI2, CCI3, CRI1,CRI2,CRI3, nrow=3)
```

grid.arrange(ind_limits_2010.histo, ind2pty_limits_2010.histo, pac_limits_2010.histo, CCI1, CCI2, CCI3, CRI1,CRI2,CRI3, nrow=3, bottom="Data from 1990-2012; in the top three graphs, 99999 indicates a state-year with no limit in that category")

>>>>

# All together now 
grid.arrange(ind_limits_2010.histo, ind2pty_limits_2010.histo, pac_limits_2010.histo, CCI1, CCI2, CCI3, CRI1,CRI2,CRI3, nrow=3, bottom="Data from 1990-2012; in the top three graphs, 99999 indicates a state-year with no limit in that category")
```
